Graph-Based Neural Reconstruction from Skeletonized 3D Networks

### 2018-01-24 papers/cvpr2018/rebuttal/egrebuttal.tex

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

%%%%%%%%% PAPER ID  - PLEASE UPDATE
\def\cvprPaperID{0446} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

\begin{document}

%%%%%%%%% TITLE - PLEASE UPDATE
\title{\LaTeX\ Guidelines for Author Response}  % **** Enter the paper title here

\maketitle
\thispagestyle{empty}

%%%%%%%%% BODY TEXT - ENTER YOUR RESPONSE BELOW
\section{Introduction}

After receiving paper reviews, authors may optionally submit a rebuttal to address the reviewers' comments, which will be limited to a {\bf one page} PDF file.  Please follow the steps and style guidelines outlined below for submitting your author response.

Note that the author rebuttal is optional and, following similar guidelines to previous CVPR conferences, it is meant to provide you with an opportunity to rebut factual errors or to supply additional information requested by the reviewers. It is NOT intended to add new contributions (theorems, algorithms, experiments) that were not included in the original submission and were not requested by the reviewers. You may optionally add a figure, graph or proof to your rebuttal to better illustrate your answer to the reviewers' comments.

The rebuttal must adhere to the same blind-submission as the original submission and must comply with this rebuttal-formatted template.

%-------------------------------------------------------------------------

\subsection{Response length}
Author responses must be no longer than 1 page in length including any references and figures.  Overlength responses will simply not be reviewed.  This includes responses where the margins and formatting are deemed to have been significantly altered from those laid down by this style guide.  Note that this \LaTeX\ guide already sets figure captions and references in a smaller font.

%------------------------------------------------------------------------
\section{Formatting your Response}

{\bf Make sure to update the paper title and paper ID in the appropriate place in the tex file.}

All text must be in a two-column format. The total allowable width of the text
area is $6\frac78$ inches (17.5 cm) wide by $8\frac78$ inches (22.54 cm) high.
Columns are to be $3\frac14$ inches (8.25 cm) wide, with a $\frac{5}{16}$ inch
(0.8 cm) space between them. The top margin should begin
1.0 inch (2.54 cm) from the top edge of the page.  The bottom margin should be
1-1/8 inches (2.86 cm) from the bottom edge of the page for $8.5 \times
11$-inch paper; for A4 paper, approximately 1-5/8 inches (4.13 cm) from the
bottom edge of the page.

Please number all of your sections and any displayed equations.  It is important
for readers to be able to refer to any particular equation.

Wherever Times is specified, Times Roman may also be used.  Main text should be
in 10-point Times, single-spaced. Section headings should be in 10 or 12 point
Times.  All paragraphs should be indented 1 pica (approx. 1/6 inch or 0.422
cm).  Figure and table captions should be 9-point Roman type as in
Figure~\ref{fig:onecol}.

%-------------------------------------------------------------------------
\subsection{References}

List and number all bibliographical references in 9-point Times, single-spaced,
at the end of your response. When referenced in the text, enclose the citation
number in square brackets, for example~\cite{Authors14}.  Where appropriate,
include the name(s) of editors of referenced books.

\begin{figure}[t]
\begin{center}
\fbox{\rule{0pt}{1.8in} \rule{0.9\linewidth}{0pt}}
   %\includegraphics[width=0.8\linewidth]{egfigure.eps}
\end{center}
   \caption{Example of caption.  It is set in Roman so that mathematics
   (always set in Roman: $B \sin A = A \sin B$) may be included without an
   ugly clash.}
\label{fig:long}
\label{fig:onecol}
\end{figure}

%-------------------------------------------------------------------------
\subsection{Illustrations, graphs, and photographs}

All graphics should be centered.  Please ensure that any point you wish to make is resolvable in a printed copy of the response.  Resize fonts in figures to match the font in the body text, and choose line widths which render effectively in print.  Many readers (and reviewers), even of an electronic copy, will choose to print your response in order to read it.  You cannot insist that they do otherwise, and therefore must not assume that they can zoom in to see tiny details on a graphic.

When placing figures in \LaTeX, it's almost always best to use \verb+\includegraphics+, and to specify the  figure width as a multiple of the line width as in the example below
{\small\begin{verbatim}
   \usepackage[dvips]{graphicx} ...
   \includegraphics[width=0.8\linewidth]
                   {myfile.eps}
\end{verbatim}
}

{\small
\bibliographystyle{ieee}
\bibliography{egbib}
}

\end{document}

### 2018-01-24 papers/cvpr2018/rebuttal/egrebuttal.tex

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

%%%%%%%%% PAPER ID  - PLEASE UPDATE
\def\cvprPaperID{0446} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

\begin{document}

%%%%%%%%% TITLE - PLEASE UPDATE
\title{Graph-Based Neural Reconstruction from Skeletonized 3D Networks}  % **** Enter the paper title here

@@

\maketitle
\thispagestyle{empty}

%%%%%%%%% BODY TEXT - ENTER YOUR RESPONSE BELOW

We would like to thank the reviewers for their time.

\section*{Reviewer 1}

\textbf{A1.} We thank the reviewer for linking to these four recent papers, although they are working on a different issue. Our algorithm works by correcting the merge errors generated by current segmentation algorithms.  The Funke et al. paper is actually a pre-paper arxiv submission for the CVPR conference. We take issue with the statement that ``the paper does not adequately reflect prior art, rendering its own conclusions questionable.'' In fact, reviewer 3 wrote as a strength ``the list of references is impressive, demonstrating comprehensive knowledge of both recent methods and the application domain''.

\textbf{A2.} This claim refers to building on-top of existing segmentation pipelines. We will clarify this point in the next revision. LASH extracts a graph from superpixels generated from a watershed. We extract a graph from this output at a different abstraction layer.

\textbf{A3.} We don't agree with the assertion that these are ``drastic'' examples but rather honest mistakes. We can easily add an additional reference for U-Net that extends the original paper to 3D. In fact, citing reference [18] for the multicut algorithm is not a mistake at all. We use the graph optimization library from Bjoern Andres\footnote{http://www.andres.sc/graph.html} which cites [18] (his own work) for the multicut package. 
We will update the reference to Funke et al. as this was a simple LaTex citation mistake.

\textbf{B1.} We agree that skeletonization can improve but our goal for this paper is to use an existing method and explore its application to new ideas.

\textbf{B2.} This is incorrect, the skeletons from the figures are from the Kasthuri et al. data.

\textbf{B3.} This is addressed in the paper. First the cubic region of interest is in nanometers, not voxels. From section 4.8, ``Since our CNN only takes as input a region of the label volume we can train on anisotropic data and test on isotropic data.'' In the same section we show the results when training on isotropic data (Fig. 9).

\textbf{B4.} We address this in the supplemental material. We can include a reference to the supplemental material in the future.

\textbf{B5.} Without the images, we avoid retraining for every new dataset that has different staining or resolution, which is every dataset that we receive from our biology collaborators. We will clarify this point in a revision.

\textbf{B6.} This analysis is provided in Sec. 4.7 and Table 2.

\textbf{B7.} We are not using ``lifted'' multicut but only the greedy-edge contraction method.

\textbf{B8. Section 3.4 states that acyclic partitionings are enforced. Since acyclic regions are not an inherent outcome of the multicut algorithm, this requires a modified multicut, but the modification is unspecified.}

\textbf{B9.} Here we reference the possibility for additional constraints using our new novel framework. Currently that enforces neurons to be acyclic but in the future can use other information. The important idea was that this framework allows domain-specific constraints.

\textbf{C1.} We use NeuroProof because it scales to terabyte datasets. Flood filling networks provide better accuracy but are 25x slower and work on a single neuron at a time. For dense reconstruction, NeuroProof is state-of-the-art. Variation of Information overcomes previous limitations of rand error and is more widely used by the community~\cite{lee2017superhuman,nunez2013machine}. The SNEMI3D dataset is considered outdated as concluded in~\cite{lee2017superhuman}.

\textbf{C2.} Most of the current state-of-the-art methods are too slow to run on very large datasets.

\section*{Reviewer 2}

Unfortunately the challenge datasets (SNEMI3D, CREMI) are too small for meaningful improvement. The datasets presented in our paper are roughly ten times the size of these challenge datasets.

\section*{Reviewer 3}

\textbf{Address acyclic nature of graph.}

There are some polynomial time algorithms for finding the general minimum spanning forest on a general graph ($O(V^2 E)$). The multicut algorithm we use has a running time of $O(V^2 log(V))$, although provides an approximation to the optimal solution. Exploring both of these algorithms is reasonable in a future revision.

### 2018-01-24 papers/cvpr2018/rebuttal/egrebuttal.tex

%%%%%%%%% BODY TEXT - ENTER YOUR RESPONSE BELOW

We would like to thank the reviewers for their time.

\section*{Reviewer 1}

\textbf{A1.} 
We thank the reviewer for showing us these four recent papers, and we will cite them in the next revision. 
However, we believe that our work focuses on a slightly different problem. 
Our algorithm corrects the split errors generated by current segmentation algorithms. 
These papers show impressive results but are fundamentally pixel-based methods whereas our method explores higher level error correction. 
We take issue with the statement that ``the paper does not adequately reflect prior art, rendering its own conclusions questionable.'' 
In fact, reviewer 3 wrote ``the list of references is impressive, demonstrating comprehensive knowledge of both recent methods and the application domain.''

\textbf{A2.} 
This claim refers to building on-top of existing segmentation pipelines. 
We will clarify this point in our revision. 
In \textit{Learning to Agglomerate Superpixel Hierarchies}, Jain et al. extract a graph from superpixels generated by a watershed algorithm. 
We, on the other hand, would use the output of \textit{LASH} as input to our framework. 
Then, We extract a graph from this input.

\textbf{A3.} 
We do not agree with the assertion that these are ``drastic'' errors but rather honest mistakes. 
In fact, citing reference [18] for the multicut algorithm is not a mistake at all. 
We use the graph optimization library from Bjoern Andres' website\footnote{http://www.andres.sc/graph.html} which cites [18] (his own work) for the multicut package. 
We will add an additional reference for U-Net that extends the original paper to 3D.
We will update the reference to Funke et al.; this was an accidental LaTex citation omission.

\textbf{B1.} 
We agree that the skeletonization algorithm can improve but our goal for this paper is to use an existing method and explore its application to new ideas.
We chose this method with its corresponding default parameters because it has been used previously for neuron skeletonization.

\textbf{B2.} 
The skeletons from the figures are actually from the anisotropic Kasthuri dataset.

\textbf{B3.} 
We address this in the paper.
The cubic region of interest is actually in nanometers, not voxels.
We further discuss this parameter in the supplemental materials (Sec. 2.1). 
In a future revision we will clarify this better.

From section 4.8, ``Since our CNN only takes as input a region of the label volume we can train on anisotropic data and test on isotropic data.'' 
In the same section we show the results when training on isotropic data (Fig. 9).

\textbf{B4.} 
We address this in the supplemental material, and will reference it in the future.

\textbf{B5.} 
Without the images, we avoid retraining for every new dataset that has different staining or resolution.
This reduces the amount of expert-labeled ground truth required for every new dataset.
In our experience with our biological collaborators, every dataset has slightly different staining so this offers a large advantage.
We will clarify our thinking.

@@

\textbf{B6.} 
This analysis is provided in Sec. 4.7 and Table 2.

\textbf{B7.} 
We are not using ``lifted'' multicut but only the greedy-edge contraction method.

\textbf{B8. Section 3.4 states that acyclic partitionings are enforced. Since acyclic regions are not an inherent outcome of the multicut algorithm, this requires a modified multicut, but the modification is unspecified.}

\textbf{B9.} 
We reference the possibility for additional constraints using our new novel framework. 
Currently we enforce neurons to be acyclic.
This is a non-trivial constraint for massive datasets where neurons span the entire volume. 
We can later extend our framework

\textbf{C1.} We use NeuroProof because it scales to terabyte datasets. 
Flood filling networks provide better accuracy but are 25x slower and work on a single neuron at a time. 
For dense reconstruction, NeuroProof is state-of-the-art. 
Variation of Information overcomes previous limitations of Rand error~\cite{lee2017superhuman,nunez2013machine}. 
The SNEMI3D dataset is outdated~\cite{lee2017superhuman}.

\textbf{C2.} Most of the current state-of-the-art methods are too slow to run on very large datasets, although we will consider other baselines in a future revision.

### 2018-01-25 papers/cvpr2018/rebuttal/egrebuttal.tex

\section*{Reviewer 2}

Unfortunately the challenge datasets (SNEMI3D, CREMI) are too small for meaningful improvement. The datasets presented in our paper are roughly ten times the size of these challenge datasets.

\section*{Reviewer 3}

\begin{figure}[h]
	\begin{center}
		\includegraphics[width=0.32\linewidth]{./figures/MSF.png}
		\caption{Error with minimum spanning forest.}
		\label{figure:msf}
	\end{center}
\end{figure}

@@

\textbf{Address acyclic nature of graph.}

Fig.~\ref{figure:msf} addresses one problem of using a minimum spanning forest where negative edges represent high affinities and positive edges represent low affinities. 
With a multicut formulation, the edge between nodes 1 and 4 will keep the blue and green segments separate.
In a minimum spanning forest nodes 1 and 4 will connect because of the moderate affinity between nodes 2 and 3.

### 2018-01-25 papers/cvpr2018/rebuttal/egrebuttal.tex

%%%%%%%%% TITLE - PLEASE UPDATE
\title{Graph-Based Neural Reconstruction from Skeletonized 3D Networks}  % **** Enter the paper title here

\maketitle
\thispagestyle{empty}

%%%%%%%%% BODY TEXT - ENTER YOUR RESPONSE BELOW

We would like to thank the reviewers for their valuable feedback.

\subsection*{Reviewer 1}

\textbf{A1.} 
We thank the reviewer for pointing out four recent papers, and we will cite them in the next revision. However, we believe that our work focuses on a slightly different problem. Our algorithm corrects the split errors generated by current segmentation algorithms. These papers show impressive results but are fundamentally pixel-based methods, whereas our method explores higher level error correction. We take issue with the statement that ``the paper does not adequately reflect prior art, rendering its own conclusions questionable.'' In fact, reviewer 3 wrote ``the list of references is impressive, demonstrating comprehensive knowledge of both recent methods and the application domain.''

\textbf{A2.} 
This claim refers to building on-top of existing segmentation pipelines. We will clarify this point in our revision. In \textit{Learning to Agglomerate Superpixel Hierarchies}, Jain et al. extract a graph from superpixels generated by a watershed algorithm. We, on the other hand, use the output of \textit{LASH} as input to our framework.

\textbf{A3.} 
We do not agree with the statement that these are ``drastic'' errors, but rather honest mistakes. In fact, citing reference [18] for the multicut algorithm was done deliberately. We use the graph optimization library from Bjoern Andres' website\footnote{http://www.andres.sc/graph.html}, which cites [18] (his own work) for the multicut package. We will add an additional reference for U-Net that extends the original paper to 3D. We will update the reference to Funke et al.

\textbf{B1.} 
We agree that the skeletonization algorithm can be improved. Our goal for this paper was to use an existing method with its corresponding default parameters because it had been used previously for neuron skeletonization. We are currently working on an improved algorithm.

\textbf{B2.} 
The skeletons shown are from an anisotropic dataset.

\textbf{B3.} 
The cubic region of interest is measured in nanometers, not voxels. We further discuss this parameter in the supplemental materials (Sec. 2.1). From section 4.8, ``Since our CNN only takes as input a region of the label volume we can train on anisotropic data and test on isotropic data.'' In the same section we show the results when training on isotropic data (Fig. 9). We will clarify this in the revision.

\textbf{B4.} 
We address this in the supplemental material, and we will reference it in the revision.

\textbf{B5.} 
Without relying on the raw images we avoid retraining for every new dataset that has different staining or resolution. This reduces the amount of expert-labeled ground truth required for training every new dataset. In our opinion this is a big advantage. We will clarify this in the revision.

@@

\textbf{B6.} 
This analysis is provided in Sec. 4.7 and Table 2.

\textbf{B7.} 
We are not using the lifted multicut.

\textbf{B8.}
The multicut algorithm does not enforce acyclic graphs but rather closed-surfaces and consistent solutions. We will update this in the next revision. We are currently working on adding additional domain-specific constraints.

\textbf{B9.} 
We mention the possibility for adding additional constraints to our framework in the future. We will clarify this in the revision.

\textbf{C1.} 
We use NeuroProof because it scales to terabyte datasets. Flood filling networks provide better accuracy but are much slower and work on a single neuron at a time. For dense reconstruction, NeuroProof is state-of-the-art. Variation of Information overcomes previous limitations of Rand error~\cite{lee2017superhuman,nunez2013machine}.

\textbf{C2.} 
Most of the current state-of-the-art methods are too slow to run on very large datasets, although we will compare against other baselines in the revision.

\subsection*{Reviewer 2}

The challenge datasets are generally too small for meaningful improvements. The datasets presented in our paper are ten times the size of these challenge datasets, and our method scales to much larger data. In a future revision, we will show the results of our network on these datasets.

\subsection*{Reviewer 3}

\begin{center}
	\includegraphics[width=0.28\linewidth]{./figures/MSF.png}
\end{center}

The figure above addresses one problem of using a minimum spanning forest, where negative and positive edges represent high and low affinities respectively. With a multicut formulation, the edge between nodes 1 and 4 will keep the blue and green segments separate. In a minimum spanning forest, nodes 1 and 4 will connect because of the moderate affinity between nodes 2 and 3.

### 2018-02-20 papers/eccv2018/paper.tex
updated paper to eccv format

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{subfig}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{caption}
%\usepackage{subcaption}
\usepackage{booktabs}
\usepackage{makecell}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{siunitx}
\usepackage{float}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

% \cvprfinalcopy % *** Uncomment this line for the final submission

\def\cvprPaperID{0446} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
%
\newcommand{\FIX}[1]{\textcolor{red}{#1}}
\newcommand{\hp}[1]{\textcolor{red}{HP: #1}}
\newcommand{\donglai}[1]{\textcolor{blue}{[Donglai: #1]}}

%% Pages are numbered in submission mode, and unnumbered in camera-ready
\ifcvprfinal\pagestyle{empty}\fi
\begin{document}

	%%%%%%%%% TITLE
	\title{Graph-Based Neural Reconstruction from Skeletonized 3D Networks}
	% Neural Reconstruction Using Skeletonized 3D Networks
	% Neural Reconstruction with Top-Down Enhancements from Skeletonized 3D Networks
	% Graph-Based Neural Reconstruction from Morphological Skeletons
	%Robust Agglomeration using 3D Skeletonization of Labeled for Connectomics}

	%\author{Brian Matejek\\
	%Harvard University\\
	%Cambridge, MA 02138, USA\\
	%{\tt\small bmatejek@seas.harvard.edu}
	%% For a paper whose authors are all at the same institution,
	%% omit the following lines up until the closing ``}''.
	%% Additional authors and addresses can be added with ``\and'',
	%% just like the second author.
	%% To save space, use either the email address or home page, not both
	%%\and
	%%Second Author\\
	%%Institution2\\
	%%First line of institution2 address\\
	%%{\tt\small secondauthor@i2.org}
	%}

	\maketitle
	%\thispagestyle{empty}
	%

	%%%%%%%%% ABSTRACT
	\begin{abstract}
		Advancements in electron microscopy image acquisition have created massive connectomics datasets in the terabyte range that make manual reconstruction of neuronal structures infeasible.
		Current state-of-the-art automatic methods segment neural membranes at the pixel level followed by agglomeration methods to create full neuron reconstructions.
		However, these approaches widely neglect global geometric properties that are inherent in the graph structure of neural wiring diagrams.
		In this work, we follow bottom-up pixel-based reconstruction by a top-down graph-based method to more accurately approximate neural pathways.
		We first generate skeletons in 3D from the neuron labels of the pixel-based segmentation.
		We then simplify this skeletonized 3D network into a 3D graph with nodes corresponding to labels from the segmentation and edges identifying potential locations of segmentation errors.
		We use a CNN classifier trained on ground truth data to generate edge weights on the 3D graph corresponding to error probabilities.
		We then apply a multicut algorithm to generate a partition on the graph that improves the final segmentation.
		Because the 3D graph is small and encodes top-down information our method is efficient and globally improves the neural reconstruction.
		We demonstrate the performance of our approach on multiple real-world connectomics datasets with an average split variation of information improvement of 19.3\%.
		%The paper provides insights into learning shape features for top-down graph-based neuron reconstruction.
	\end{abstract}
	%%%%%%%%	% BODY TEXT

@@

	{\small
		\bibliographystyle{ieee}
		\bibliography{paper}}

>>>>

% last updated in April 2002 by Antje Endemann
% Based on CVPR 07 and LNCS, with modifications by DAF, AZ and elle, 2008 and AA, 2010, and CC, 2011; TT, 2014; AAS, 2016

\documentclass[runningheads]{llncs}
\usepackage{graphicx}
\usepackage{amsmath,amssymb} % define this before the line numbering.
\usepackage{ruler}
\usepackage{color}
\usepackage{subfig}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{caption}
%\usepackage{subcaption}
\usepackage{booktabs}
\usepackage{makecell}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{siunitx}
\usepackage{float}
\usepackage[width=122mm,left=12mm,paperwidth=146mm,height=193mm,top=12mm,paperheight=217mm]{geometry}

\begin{document}
% \renewcommand\thelinenumber{\color[rgb]{0.2,0.5,0.8}\normalfont\sffamily\scriptsize\arabic{linenumber}\color[rgb]{0,0,0}}
% \renewcommand\makeLineNumber {\hss\thelinenumber\ \hspace{6mm} \rlap{\hskip\textwidth\ \hspace{6.5mm}\thelinenumber}}
% \linenumbers
\pagestyle{headings}
\mainmatter
\def\ECCV18SubNumber{***}  % Insert your submission number here

\titlerunning{ECCV-18 submission ID \ECCV18SubNumber}

\authorrunning{ECCV-18 submission ID \ECCV18SubNumber}

\title{Graph-Based Neural Reconstruction from Skeletonized 3D Networks}

\author{Anonymous ECCV submission}
\institute{Paper ID \ECCV18SubNumber}

\maketitle

\begin{abstract}
Advancements in electron microscopy image acquisition have created massive connectomics datasets in the terabyte range that make manual reconstruction of neuronal structures infeasible.
Current state-of-the-art automatic methods segment neural membranes at the pixel level followed by agglomeration methods to create full neuron reconstructions.
However, these approaches widely neglect global geometric properties that are inherent in the graph structure of neural wiring diagrams.
In this work, we follow bottom-up pixel-based reconstruction by a top-down graph-based method to more accurately approximate neural pathways.
We first generate skeletons in 3D from the neuron labels of the pixel-based segmentation.
We then simplify this skeletonized 3D network into a 3D graph with nodes corresponding to labels from the segmentation and edges identifying potential locations of segmentation errors.
We use a CNN classifier trained on ground truth data to generate edge weights on the 3D graph corresponding to error probabilities.
We then apply a multicut algorithm to generate a partition on the graph that improves the final segmentation.
Because the 3D graph is small and encodes top-down information our method is efficient and globally improves the neural reconstruction.
We demonstrate the performance of our approach on multiple real-world connectomics datasets with an average split variation of information improvement of 19.3\%.
\keywords{connectomics, skeletonization, deep learning}
\end{abstract}

@@

\clearpage

\bibliographystyle{splncs}
\bibliography{egbib}
